---
title: "Janitor Package"
subtitle: "Cleaning dirty data using the janitor package - by Eduardo Campbell and Claudia Zwar"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
    css: custom.css 
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro to the janitor package

As a budding data scientist, do you feel like you spend a lot of time **tidying** data? Renaming columns, deleting unnecessary information, wrangling data into `tidy data` format? If your answer to this question is yes, this session is for you.

Today we will introduce you to the janitor package, which is part of the tidyverse. The janitor package was designed to help with some of the repetitive tasks involved in preparing data for analysis, and quickly looking at aspects of data (e.g. with tables).

What we will cover in this session:

* Cleaning a dirty dataset using janitor
* Creating tables
* Editing tables and data frames using janitor functions 

## Cleaning dirty datasets using janitor

For this exercise, we are going to use an archetypal 'dirty' data set, which we created for this exercise. The data contains information about attendees of a Hertie School end of year party. 

```{r, message=F}
#
```

## Creating tables

```{r, message=F}
#
```

## Editing tables and data frames

```{r, message=F}
#
```
